Self Regulation Ontology Retest Analyses

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

@@

Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)

### Conceptual replications 
- Larger reliability estimates for surveys
- Larger variance in reliability estimates for tasks

### Sample size effects/publication bias

Deviance between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results.

@@

```{r}
lit_review %>%
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')

mod1 = lmer(retest_reliability~sample_size+(1|dv), data=lit_review)

```{r}
#sd by average sample size
lit_review %>%
  group_by(dv) %>%
  summarise(sd_rel = sd(retest_reliability),
            avg_sample_size = mean(sample_size)) %>%
  ggplot(aes(avg_sample_size, sd_rel))+
  geom_point()+
  xlim(0,200)
```

>>>>

Tasks have significantly lower reliability and reliability decreases with increasing sample size.

@@

Conceptual replication 1: Compare effect sizes of effect of task on reliability estimates in literature vs our results (just looking at the variables you find in the literature)

```{r}
m1 = rel_comp %>% filter(task == "task") %>% summarise(m1 = mean(retest_reliability))
m2 = rel_comp %>% filter(task == "survey") %>% summarise(m2 = mean(retest_reliability))
n1 = nrow(rel_comp %>% filter(task == "task"))
n2 = nrow(rel_comp %>% filter(task == "survey"))
var1 = rel_comp %>% filter(task == "task") %>% summarise(var1 = var(retest_reliability))
var2 = rel_comp %>% filter(task == "survey") %>% summarise(var1 = var(retest_reliability))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_lit = abs(m1-m2)/sd_pooled
d_lit
```

The literature review conceptually replicates our finding of lower reliability estimates for task measures but with a much smaller effect size.

```{r}
n_df = rel_comp %>% 
  group_by(dv) %>%
  tally()

boot_comp = data.frame()

for(i in 1:length(unique(rel_comp$dv)) ){
  cur_dv = unique(rel_comp$dv)[i]
  n = n_df$n[n_df$dv == cur_dv]
  sample_df = boot_df %>% filter(dv == cur_dv)
  tmp = sample_n(sample_df, n)
  boot_comp = rbind(boot_comp, tmp)
}

rm(cur_dv, n, sample_df, tmp)

boot_comp = boot_comp %>%
  mutate(task=ifelse(grepl("survey", dv), "task", "survey"))

m1 = boot_comp %>% filter(task == "task") %>% summarise(m1 = mean(icc))
m2 = boot_comp %>% filter(task == "survey") %>% summarise(m2 = mean(icc))
n1 = nrow(boot_comp %>% filter(task == "task"))
n2 = nrow(boot_comp %>% filter(task == "survey"))
var1 = boot_comp %>% filter(task == "task") %>% summarise(var1 = var(icc))
var2 = boot_comp %>% filter(task == "survey") %>% summarise(var1 = var(icc))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_boot = abs(m1-m2)/sd_pooled
d_boot
```

Conceptual replication 2: Larger variance in reliability estimates for tasks

```{r}
tmp = rel_comp %>%
  group_by(dv) %>%
  summarise(rel_var = var(retest_reliability), 
            task=unique(task)) %>%
  na.omit()
tmp %>%
  ggplot(aes(rel_var, fill=task))+
  geom_density(alpha=0.5, position='identity')+
  theme(legend.title = element_blank())+
  xlab('Variance of reliability estimates')
```

```{r}
summary(lm(rel_var ~ task, tmp))
```

Effect sizes of task on variance in reliability estimates in literature vs our results are comparable

```{r}
m1 = tmp %>% filter(task == "task") %>% summarise(m1 = mean(rel_var))
m2 = tmp %>% filter(task == "survey") %>% summarise(m2 = mean(rel_var))
n1 = nrow(tmp %>% filter(task == "task"))
n2 = nrow(tmp %>% filter(task == "survey"))
var1 = tmp %>% filter(task == "task") %>% summarise(var1 = var(rel_var))
var2 = tmp %>% filter(task == "survey") %>% summarise(var2 = var(rel_var))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_lit = abs(m1-m2)/sd_pooled
d_lit
```

```{r}
tmp = boot_comp %>%
  group_by(dv) %>%
  summarise(rel_var = var(icc), 
            task=unique(task)) %>%
  na.omit()

m1 = tmp %>% filter(task == "task") %>% summarise(m1 = mean(rel_var))
m2 = tmp %>% filter(task == "survey") %>% summarise(m2 = mean(rel_var))
n1 = nrow(tmp %>% filter(task == "task"))
n2 = nrow(tmp %>% filter(task == "survey"))
var1 = tmp %>% filter(task == "task") %>% summarise(var1 = var(rel_var))
var2 = tmp %>% filter(task == "survey") %>% summarise(var2 = var(rel_var))
sd_pooled = sqrt(((n1-1)*var1+(n2-1)*var2)/(n1+n2-2))
d_boot = abs(m1-m2)/sd_pooled
d_boot
```

Square difference between our mean estimate and the reliability from the literature decreases exponentially with sample size. The smaller the sample size in the literature the more the reliability estimate differs from our results.

@@
